Machine Learning Methods for Site-specific Input Management

### 2022-02-06 Codes/PrepareResults.rmd
set figure options

@@

>>>>

# Set the figure options
```{r figure_setup, cache = F}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

@@

```{r}
source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")

pCorn <- price_table[2, pCorn]
pN <- price_table[2, pN]

# /*=================================================*/
#' # Field Data Sets
# /*=================================================*/

# /*----------------------------------*/
#' ## (1) cell-level data set
# /*----------------------------------*/
# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))

coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))

x <- 1
coef_data_m <- coef_data[sim == x, ]
coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]

sample_dt_cell <- prepare_raw_data(x, field = field, coef_data_m = coef_data_m, coef_data_t = coef_data_t, app_error = "no") %>%
  .$reg_raw_data

field_cell_sf <-
  left_join(select(field, unique_cell_id), field_cell_dt, by = "unique_cell_id") %>%
  na.omit() %>%
  mutate(plot_id = ceiling(subplot_id / 4)) %>%
  filter(padding == 1)

saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))

# /*----------------------------------*/
#' ## (2) subplot-level field without padding area
# /*----------------------------------*/

field_subplot_sf <-
  field_cell_sf %>%
  group_by(subplot_id, strip_id) %>%
  summarise(
    sim = mean(sim),
    yield = mean(yield),
    opt_N = mean(opt_N),
    rate = mean(rate),
    aa_n = mean(aa_n),
    alpha = mean(alpha),
    beta = mean(beta),
    ymax = mean(ymax),
    alpha1 = mean(alpha1),
    alpha2 = mean(alpha2),
    beta1 = mean(beta1),
    beta2 = mean(beta2),
    ymax1 = mean(ymax1),
    ymax2 = mean(ymax2),
    theta_1 = mean(theta_1),
    theta_2 = mean(theta_2)
  ) %>%
  mutate(unique_subplot_id = paste0(strip_id, "_", subplot_id)) %>%
  select(!c(strip_id, subplot_id))

saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
```
